---
title: "Mario_Poster"
author: "Jon Kaplan"
date: "9/11/2019"
output: html_document
---

#libraries
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(ggplot2)
#library(devtools)
#devtools::install_github('cttobin/ggthemr')
library(ggthemr)
library(data.table)
library(corrplot)
library(lubridate)
library(dplyr)
library(plyr)
library(ggpubr)

```


# load data
```{r cars}
#videogamesales <- read.csv("vgsales.csv")

videogamesales <- read.csv("CleanVG.csv", na.strings=c("", "NA")) #16719
videogamesales$Year_of_Release <- as.Date(videogamesales$Year_of_Release, "%Y")
videogamesales$Year_of_Release <- format(as.Date(videogamesales$Year_of_Release, format="%d/%m/%Y"),"%Y")
#videogamesales <- na.omit(videogamesales) #6947
```

clean data
```{r}
videogamesalesclean <- na.omit(videogamesales)
videogamesalesclean$Year_of_Release <- as.Date(videogamesalesclean$Year_of_Release, "%Y")
videogamesalesclean$Year_of_Release <- format(as.Date(videogamesalesclean$Year_of_Release, format="%d/%m/%Y"),"%Y")

genrecount <- count(videogamesales$Genre)
p<-ggplot(data=genrecount, aes(x=x, y=freq)) +
  geom_bar(stat="identity")+
  geom_text(aes(label=freq), vjust=1.6, color="white", size=3.5)
p+coord_flip()
```


Color scheme

```{r}
mario_colours <- c('#5311A6', '#DC0442', '#60D904', '#F4E005', '#310666', '#870027', '#3A8500', '#968900')
# you have to add a colour at the start of your palette for outlining boxes, we'll use a grey:
mario_with_grey <- c("#555555", mario_colours)
# remove previous effects:
#ggthemr_reset()
# Define colours for your figures with define_palette
mario_theme <- define_palette(
 swatch = mario_with_grey, # colours for plotting points and bars
 gradient = c(lower = mario_colours[1L], upper = mario_colours[2L]), #upper and lower colours for continuous colours
 background = "#EEEEEE" #defining a grey-ish background
)
# set the theme for your figures:
ggthemr(mario_theme)

```



subdata
```{r}
#videogamesales <- videogamesales %>% mutate(highlyreviewed=if_else(Critic_Score>quantile(Critic_Score, .95), 1, 0))
#videogamesales <- videogamesales %>% mutate(topselling=if_else(Global_Sales>quantile(Global_Sales, .95), 1, 0))
#videogamesales$highlyreviewed <- as.factor(videogamesales$highlyreviewed)
#videogamesales$topselling <- as.factor(videogamesales$topselling)
#elitegames <- videogamesales %>% filter(highlyreviewed ==1, topselling==1) 
#topselling <- videogamesales %>% filter(topselling == 1)
#highrated <- videogamesales %>% filter(highlyreviewed == 1)
nintendo <- filter(videogamesales, Publisher == "Nintendo") 
nintendo_developer <- filter(videogamesales, Developer == "Nintendo") 
platformers <- videogamesales %>%  filter(Genre == 'Platform') #888 games

nintendoplatformers <- platformers %>% filter(Publisher == "Nintendo") #nintendo has 112 platformer games
nintendo_esrb <- nintendo %>% filter(Rating != "NA")
#ea_publisher <- filter(elitegames, Publisher == "Electronic Arts") 
# critic score
#292 of 331 high rated games are Nintendo


#mario
mariogames <- videogamesales %>% mutate(Is_Mario = str_extract(Name, "Mario") =='Mario' )
mariogames <- mariogames %>% filter(Is_Mario == TRUE) #53 mario games total
marioplatformers <-  platformers %>%  mutate(Is_Mario = str_extract(Name, "Mario") =='Mario' )
marioplatformers <- marioplatformers %>% filter(Is_Mario == TRUE) #33 mario games that are platformers

#zelda
zeldagames <- videogamesales %>% mutate(Is_Zelda = str_extract(Name, "Zelda") =='Zelda' )
zeldagames <- zeldagames %>% filter(Is_Zelda == TRUE) #27 zelda games

#pokemon
pokemongames <- videogamesales %>% mutate(Is_Pokemon = str_extract(Name, "Pokemon") =='Pokemon' )
pokemongames <- pokemongames %>% filter(Is_Pokemon == TRUE) #36 pokemon games


#donkeykong
donkeygames <- videogamesales %>% mutate(Is_Donkey = str_extract(Name, "Donkey") =='Donkey' )
donkeygames <- donkeygames %>% filter(Is_Donkey == TRUE) #15 donkey games

#yoshi
yoshigames <- videogamesales %>% mutate(Is_Yoshi = str_extract(Name, "Yoshi") =='Yoshi' )
yoshigames <- yoshigames %>% filter(Is_Yoshi == TRUE) #68 yoshi games

#kirby
kirbygames <- videogamesales %>% mutate(Is_Kirby = str_extract(Name, "Kirby") =='Kirby' )
kirbygames <- kirbygames %>% filter(Is_Kirby == TRUE) #96 kirby games

#animalcrossing
acgames <- videogamesales %>% mutate(Is_AC = str_extract(Name, "Animal Crossing") =='Animal Crossing' )
acgames <- acgames %>% filter(Is_AC == TRUE) #24 animal crossing games

#metroid
metroidgames <- videogamesales %>% mutate(Is_Metroid = str_extract(Name, "Metroid") =='Metroid' )
metroidgames <- metroidgames %>% filter(Is_Metroid == TRUE) #56 metroid games

#fireemblem
fireemblemgames <- videogamesales %>% mutate(Is_Fire = str_extract(Name, "Fire Emblem") =='Fire Emblem' )
fireemblemgames <- fireemblemgames %>% filter(Is_Fire == TRUE) #52 fire emblem games

#supersmashbros
smashgames <- videogamesales %>% mutate(Is_Smash = str_extract(Name, "Smash Bros") =='Smash Bros' )
smashgames <- smashgames %>% filter(Is_Smash == TRUE) #20 super smash bros games

#starfox
stargames <- videogamesales %>% mutate(Is_Star = str_extract(Name, "Star Fox") =='Star Fox' )
stargames <- stargames %>% filter(Is_Star == TRUE) #28 star fox games

#layton
#starfox
laytongames <- videogamesales %>% mutate(Is_Layton = str_extract(Name, "Layton") =='Layton' )
laytongames <- laytongames %>% filter(Is_Layton == TRUE) #28 star fox games



#wii series
wiiseries <- videogamesales %>% mutate(Is_Wii = str_extract(Name, "Wii ") =='Wii ' )
#wiiseries <- videogamesales %>% mutate(Is_Wii = str_extract(Name, "Wii Fit") =='Wii Fitt' )
wiiseries <- wiiseries %>% filter(Is_Wii == TRUE) #28 star fox games
tbl <- tbl_df(wiiseries) %>%
  group_by(Name) %>%
  tally(Global_Sales) %>%
  top_n(10)

#franchises
videogamesales <- videogamesales %>% mutate(Is_Mario = str_extract(Name, "Mario") =='Mario' )
#videogamesales <- videogamesales %>% mutate(Is_Donkey = str_extract(Name, "Donkey") =='Donkey' )
videogamesales <- videogamesales %>% mutate(Is_Zelda = str_extract(Name, "Zelda") =='Zelda' )
videogamesales <- videogamesales %>% mutate(Is_Pokemon = str_extract(Name, "Pokemon") =='Pokemon' )
franchises <- videogamesales %>% filter(Is_Pokemon ==TRUE | Is_Zelda==TRUE | Is_Mario==TRUE)
```








franchise stats
```{r}
#Global stats
mean(franchises$Global_Sales) #4.755 average global sales
sum(franchises$Global_Sales) #846.4 total (10% of all total video game sales)

# NA stats
mean(franchises$NA_Sales) # 2.26 average NA sales
sum(franchises$NA_Sales) # 402.05 NA sales

# JP stats
mean(franchises$JP_Sales) # 1.11 average JP sales
sum(franchises$JP_Sales) # 198.3 JP sales

#europe stats
mean(franchises$EU_Sales) # 1.135 average EU sales
sum(franchises$EU_Sales) #202 EU sales

#franchise platformers

# franchises averages
mean(mariogames$Global_Sales) #  4.821826
mean(zeldagames$Global_Sales) # 3.054444
mean(pokemongames$Global_Sales) # 5.817222
mean(marioplatformers$Global_Sales) # 9.132727
mean(donkeygames$Global_Sales) # 1.960882
mean(platformers$Global_Sales) # 0.9325225

# franchises sums
sum(acgames$Global_Sales) #130.36
sum(pokemongames$Global_Sales) # 209.42
sum(mariogames$Global_Sales) # 554.51
sum(zeldagames$Global_Sales) # 82.47
sum(marioplatformers$Global_Sales) # 301.38
sum(donkeygames$Global_Sales) #66.67
sum(kirbygames$Global_Sales) #149.12
sum(yoshigames$Global_Sales) #88.36
sum(metroidgames$Global_Sales) #71.76
# Mario Games (non-Platformer) 253.13

#846.4 total franchise sum



209.42/846.4 #24.74% for pokemon games
554/846.4 # 65.45% for mario games
82.47/846.4 # 10.00 for zelda games
253.13/846.4 #29.90% for mario games (non-platformer)
301.38/846.4 #35.61% for mario platformer games
66.67/846.4 # 8.00% for donkey kong


209.42+554.51+82.47+66.67+149.12+88.36

#notable nintendo franchises 
130.36+209.42+554.51+82.47+66.67+149.12+88.36 #1352.67 total 8 franchise global sales
130.36/1352.67 #9.63 for animal crossing
209.42/1352.67 #15.48% for pokemon games
554.51/1352.67 #41.00% for mario games
82.47/1352.67 #6.10% for zelda games
66.67/1352.67#4.93% for dk games
149.12/1352.67 #11.02& for kirby games
88.36/1352.67 #6.53 for yoshi games
71.76/1352.67 #5.30% for metroid games


# top 10 nintendo franchises pie chart
sum(acgames$Global_Sales) #130.36
sum(pokemongames$Global_Sales) # 209.42
sum(mariogames$Global_Sales) # 554.51
sum(zeldagames$Global_Sales) # 82.47
sum(marioplatformers$Global_Sales) # 301.38
sum(donkeygames$Global_Sales) #66.67
sum(kirbygames$Global_Sales) #149.12
sum(metroidgames$Global_Sales) #71.76
sum(stargames$Global_Sales) #47.2
sum(yoshigames$Global_Sales) #88.36
sum(smashgames$Global_Sales) #152.52
sum(fireemblemgames$Global_Sales) #38.08
# wii sports 205.24 total, 11 games, 18.66 average

# top 10 nintendo franchises
sum(videogamesales$Global_Sales) #35280.08

#kirby
149.12

# top 5 nintendo game franchises
#mario
554.51/1331.18 #41.65% mario

# super smash bros
152.52/1331.18 #11.46% super smash

# pokemon games
209.42/1331.18 #15.73% pokemon

# wii sports
205.24/1331.18 #15.42% wii sports games

# animal crossing
209.49/1331.18 #15.74% animal crossing games

#total is 1331.18
554.51+152.52+209.42+205.24+209.49




```


games summary stats
```{r}
mean(videogamesales$Global_Sales) # 0.53 average global sales
sum(videogamesales$Global_Sales) #8920.3 total global sales
mean(videogamesalesclean$Critic_Score) # 70.26357 average critic score
```

elite games
```{r}
nintendoelitegames <- elitegames %>% filter(Developer == "Nintendo") # nintendo has 10 elite games as developer and 14 games as publisher

mean(elitegames$Global_Sales) # 6.493482 average global sales for elite games
mean(elitegames$Critic_Score) # 93.30357 avereage critic score for elite games


```

topselling
```{r}
mean(topselling$Critic_Score) #84.49 average critic score of game that is in top 5% of global sales
mean(topselling$Global_Sales) # average global sales for top selling game is 6.26

```

highrated
```{r}
#highrated <- videogamesales %>% filter(highlyreviewed == 1)
#ea_publisher <- filter(highrated, Developer == "EA") 
#highratednintendo <- 

# nintendo has 30 of 331 highrated games as publisher (582 total publishers)
# nintendo has 13 of 331 highrated games as developer (1696 total developers)
# EA has 0 highrated games in 95% critic wise
mariogameshighrated <- highrated %>% mutate(Is_Mario = str_extract(Name, "Mario") =='Mario' )


mariogameshighrated <- mariogameshighrated %>% filter(Is_Mario == TRUE) 

highratednintendo <- highrated %>% filter(Publisher=="Nintendo")
  
mean(mariogames$Critic_Score) # 77.11 average critic score of mario game
mean(mariogames$Global_Sales) # 5.15 average global sales of mario game
mean(marioplatformers$Global_Sales) # 9.80 average global sales of mario platformer game
mean(marioplatformers$Critic_Score) # 88.31 average critic score of mario platformer game
mean(highrated$Critic_Score) #92.30 top 5% of games
mean(highratednintendo$Critic_Score) #92.60 for nintendo highly rated games
mean(highrated$Global_Sales) #high rated game has average global sales of 2.85 
platformershighrated <- highrated %>% filter(Genre == "Platform")

```



genre stats
```{r}

sum(nintendoconsoles$Global_Sales)

```
mario games
```{r}
#all mario games
mean(mariogames$Global_Sales) #5.15 average global sales
mean(mariogames$Critic_Score) #77.11 average critic score


#mario platformers
mean(marioplatformers$Global_Sales) # 9.798462 average global sales
mean(marioplatformers$Critic_Score) # 88.31 average critic score

```




get percentages 
```{r}

marioplatformerscount <- count(marioplatformers$Genre)
marioplatformers = mutate(marioplatformers, 
                genre_pct = marioplatformers$Genre / count(marioplatformers$Genre),
                sales_pct = marioplatformers$Global_Sales / sum(marioplatformers$Global_Sales))


marioplatformers
```
donut chart
```{r}
ggdonutchart(df, "value", label = "group")

ggdonutchart(marioplatformers, marioplatformers$Global_Sales, label=marioplatformers$Name)



ggdonutchart(nintendoconsolesgenres, "Var2", label="Freq")
# Change color
# ++++++++++++++++++++++++++++++++

# Change fill color by group
# set line color to white
# Use custom color palette
 ggdonutchart(platformers, "value", label = "group",
      fill = "", color = "white",
       palette = c("#00AFBB", "#E7B800", "#FC4E07") )


# Change label
# ++++++++++++++++++++++++++++++++

# Show group names and value as labels
labs <- paste0(df$group, " (", df$value, "%)")
ggdonutchart(df, "value", label = labs,
   fill = "group", color = "white",
   palette = c("#00AFBB", "#E7B800", "#FC4E07"))

# Change the position and font color of labels
ggdonutchart(df, "value", label = labs,
   lab.pos = "in", lab.font = "white",
   fill = "group", color = "white",
   palette = c("#00AFBB", "#E7B800", "#FC4E07"))

```


console revenue per console
```{r}

```

nintendo games
```{r}
#292 nintendo games
mean(nintendo$Global_Sales) # 2.91 average global sales as Nintendo publisher
mean(nintendo$Critic_Score) # 76.27 average critic score as Nintendo publisher

mean(nintendo_developer$Global_Sales) #  7.792647 average global sales as Nintendo developer
mean(nintendo_developer$Critic_Score) # 80.47059 average critic score as Nintendo developer

```

Nintendo sales trend time series
```{r}
#time seris
ggplot(nintendo, aes(Year_of_Release, Global_Sales)) +
           geom_point(na.rm=TRUE)
```



pie charts
```{r}
ggdonutchart(genreplatform, Genre, label = x, lab.pos = c("out", "in"),
  lab.adjust = 0, lab.font = c(4, "bold", "black"), font.family = "",
  color = "black", fill = "white", palette = NULL, size = NULL)




genreplatform <- count(nintendo, c("Genre", "Platform", "Year_of_Release"))

```


platformers

```{r}
PlatFormers <- videogamesales %>%  filter(Genre == 'Platform')
# make new column is mario in the name? boolean. Compare both....
######################################################
# mutate new column
PlatFormers1 <- PlatFormers
PlatFormers1 <-  PlatFormers %>%  mutate(Is_Mario = str_extract(Name, "Mario") =='Mario' )
PlatFormers1[PlatFormers1$Is_Mario == NA,] <- FALSE
PlatFormers1$Is_Mario[is.na(PlatFormers1$Is_Mario)] <- "FALSE"
is.factor(PlatFormers1$Is_Mario)
PlatFormers1$Is_Mario <- as.factor(PlatFormers1$Is_Mario)
PlatFormers1$Year_of_Release <- as.numeric(PlatFormers1$Year_of_Release)
PlatFormers2 <- PlatFormers1 %>%  filter(Year_of_Release >= 1985)
ggplot(PlatFormers1, aes(x = Year_of_Release, y = Global_Sales, fill = Is_Mario)) + geom_col()
ggplot(PlatFormers2, aes(x = Year_of_Release, y = Global_Sales)) + geom_line()

```


platformer jon
```{r}
platformersnonmario <- videogamesales %>%  filter(Is_Mario == NA) 

platformersnonmario <- videogamesales %>%
    select(-Platformers) 
marioplatformers <-  platformers %>%  mutate(Is_Mario = str_extract(Name, "Mario") =='Mario' )
marioplatformers <- marioplatformers %>% filter(Is_Mario == TRUE)


sum(marioplatformers$Global_Sales) #301.38
sum(nintendoconsoles$Global_Sales) #1937.24

nintendoconsolesgenres <- as.data.frame(table(nintendoconsoles$Genre, nintendoconsoles$Global_Sales))

unique(platformers$Genre)

#NINTENDO PLATFORMER STAT
sum(nintendoplatformers$Global_Sales) #425.94
sum(platformers$Global_Sales) #825.08
425.94/825.08 #51.62% nintendo platofrmers marketshare of all platformers


#NINTENDO HANDHELD STAT
sum(videogamesales$Global_Sales) #35280.08
sum(handheld$Global_Sales) #1988.6
sum(nintendohandhelds$Global_Sales) #1640.14
sum(nintendoconsoles$Global_Sales) #1937.24

unique(nintendoconsoles$Platform)


```



heatmap
```{r}
 nba.m <- ddply(nba.m, .(variable), transform,
+     rescale = rescale(value))

elitemelt <- ddply(videogamesales, .(Genre), transform, rescale = rescale(value))


p <- ggplot(elitegames, aes(Genre, Name)) + geom_tile(aes(fill = ), colour = "white") + scale_fill_gradient(low = "white", high = "steelblue"))

```

```{r}

colnames(elitegames) <- with(prDes, paste(devStage, gType, sidChar, sep = "_"))
```


subsets
```{r}
library(ggplot2)
vgsales <- read.csv("CleanVG.csv")
#sum(sport$NA_Sales) = '95.29'
#sum(sport$EU_Sales) = '89.99'
#sum(sport$JP_Sales) = '14.67'

#subset(VideoGames,Genre == 'Action')
#action=subset(VideoGames,Genre == 'Action')

#sum(action$NA_Sales) = '134.38'
#sum(action$EU_Sales) = '99.62'
#sum(action$JP_Sales) = '19.69'

#fight=subset(VideoGames,Genre =='Fighting')
#sum(fight$NA_Sales) = '25.35'
#sum(fight$EU_Sales) = '10.54'
#sum(fight$JP_Sales) = '14.07'

#platform=subset(VideoGames,Genre =='Platform')
#sum(platform$NA_Sales) = '183.82'
#sum(platform$EU_Sales) = '75.58' 
#sum(platform$JP_Sales) = '61.99'

#race=subset(VideoGames,Genre =='Racing')
#sum(race$NA_Sales) = '79.05'
#sum(race$EU_Sales) = '58.06'
#sum(race$JP_Sales) = '28.03'

#roleplay=subset(VideoGames,Genre =='Role-Playing')
#sum(roleplay$NA_Sales) = '105.72'
#sum(roleplay$EU_Sales) = '79.41' 
#sum(roleplay$JP_Sales) = '90.31'

#shoot=subset(VideoGames,Genre =='Shooter')
#sum(shoot$NA_Sales) = '200.48'
#sum(shoot$EU_Sales) = '98.12'
#sum(shoot$JP_Sales) = '5.87'
```
=


handheld
```{r}
unique(videogamesales$Platform)

#handhelds <- ("GB", "DS", "GBA", "3DS", "PSP", "PSV", "GG")
handheld <- videogamesales %>% filter(Platform == "GB" | Platform == "DS" | Platform == "GBA" | Platform == "3DS" | Platform == "PSP" | Platform == "PSV" | Platform == "GG")
nintendohandhelds <- videogamesales %>% filter(Platform == "GB" | Platform == "DS" | Platform == "GBA" | Platform == "3DS")



# nintendo marketshare of handhelds
sum(handheld$Global_Sales) # 1988.56 total global sales for handhelds
sum(nintendohandhelds$Global_Sales) # 1640.14 
# 82.48% of all handheld marketshare

mean(handheld$Global_Sales) # 0.3800038
mean(nintendohandhelds$Global_Sales) # 0.4566091

table(handheld$Platform)

520+2152+98+822 #3592 Nintendo handheld games

3592/5234 #Nintendo comprises 68.63% of all handheld games on market

1209+432 #1641 playstation handheld games
#348.42 total global sales
# 0.21 average

#handheld vs console
sum(videogamesales$Global_Sales) #8920.3 all console sales

sum(nintendoconsoles$Global_Sales) #1937.24 nintendo consoles sales
sum(nintendohandhelds$Global_Sales) # 1640.14 

1640.14/1937.24 #84.66% of nintendos sales come from its handhelds

nphandheld <- nintendohandhelds %>% filter(Genre == "Platformers")

unique(nintendoconsoles$)
```



correlation sales
```{r}
columns = c("Global_Sales", "NA_Sales", "EU_Sales", "JP_Sales", "Other_Sales")
vgamesVariables <- videogamesales[, columns]
res <- cor(vgamesVariables)
round(res, 2)

#correlation
M <- cor(videogamesales[, columns])
corrplot(M, method="circle")
```


global sales by genre
```{r}
library(dplyr)
library(ggplot2)
#Histogram of Global sales of the game by genre
revenue_by_Genre=aggregate(Global_Sales~Genre,videogamesales,sum)
arrange_by_Genre=arrange(revenue_by_Genre,desc(Global_Sales))
arrange_by_Genre$Genre = factor(arrange_by_Genre$Genre, levels = arrange_by_Genre$Genre)
ggplot(arrange_by_Genre,aes(Genre,Global_Sales)) + 
  geom_bar(fill="blue",stat = "identity") +
  ggtitle("Video Game - Global Sales by Genre")
```

global sales by ERB rating
```{r}
library(dplyr)
library(ggplot2)
#Histogram of Global sales of the game by genre
revenue_by_Rating=aggregate(Global_Sales~Rating,videogamesales,sum)
arrange_by_Rating=arrange(revenue_by_Rating,desc(Global_Sales))
arrange_by_Rating$Rating = factor(arrange_by_Rating$Rating, levels = arrange_by_Rating$Rating)

par(mfrow=c(2,2))
revenue_by_Rating=aggregate(Global_Sales~Rating,videogamesales,sum)
arrange_by_Rating=arrange(revenue_by_Rating,desc(Global_Sales))
arrange_by_Rating$Rating = factor(arrange_by_Rating$Rating, levels = arrange_by_Rating$Rating)
ggplot(arrange_by_Rating,aes(Rating,Global_Sales)) + 
  geom_bar(fill="blue",stat = "identity") +
  ggtitle("Video Game - Global Sales by ESRB Rating (all games)")
revenue_by_Rating=aggregate(Global_Sales~Rating,highrated,sum)
arrange_by_Rating=arrange(revenue_by_Rating,desc(Global_Sales))
arrange_by_Rating$Rating = factor(arrange_by_Rating$Rating, levels = arrange_by_Rating$Rating)
ggplot(arrange_by_Rating,aes(Rating,Global_Sales)) + 
  geom_bar(fill="blue",stat = "identity") +
  ggtitle("Video Game - Global Sales by ESRB Rating (High-rated games)")

```


reshape
```{r}
library(reshape2)
vg.long<-melt(means,id.vars="gender")
```


Percent barchart
```{r}

percent_wall_type <- videogamesales %>%
  count("Publisher", "Global_Sales") %>%
  group_by("Publisher") %>%
  mutate(percent = n / sum(n)) %>%
  ungroup()

ggplot(countgenres, aes(x = Genre, y = n, fill = n) +
     geom_bar(stat = "identity", position = "dodge"))
```

mario platformers marketshare within nintendo
```{r}
marioplatformers #33 games
sum(marioplatformers$Global_Sales) #301.38
mean(marioplatformers$Global_Sales) #9.13 average mario platformer sales
nintendoconsoles_pl <- nintendoconsoles %>% filter(Genre=="Platform") #310 platformers
sum(nintendoconsoles_pl$Global_Sales) #274.1
mean(nintendoconsoles_pl$Global_Sales) #0.88 average sales for non-mario platform on nintendo consoles

sum(mariogames$Global_Sales) #554.51
sum(nintendoconsoles$Global_Sales) #1937.24
554.51/1937.24 #mario games make up 28.62% of all global sales from games on Nintendo consoles

```

percentages genre
```{r}
ggdonutchart(countgenres, "freq", label = "Genre==Platform")


co
#all genres
library(magrittr)
countgenres <- videogamesales  %>% 
  dplyr::group_by(Genre, Global_Sales) %>%
  dplyr::summarise(n = n()) %>%
  mutate(freq = n / sum(n))

nintendoplatformers


videogamesales %>% count(Genre, Global_Sales) %>% summarise(n=n()) %>% mutate(freq = n/sum(n))

```
Nintendo ESRB ratings by genre
```{r}

nintendoconsoles <- videogamesales %>% filter(Platform == "GB" | Platform == "DS" | Platform == "GBA" | Platform == "3DS" | Platform == "Wii" | Platform == "NES" | Platform == "SNES" | Platform == "N64" | Platform == "WiiU" | Platform == "GC")


nintendoconsoles$Rating <- factor(nintendoconsoles$Rating, levels=c(levels="E", "E10+", "T", "M"))

levels(nintendoconsoles$Rating)

#nintendo_esrb$Rating <- factor(nintendo_esrb$Rating, levels=c(levels="E", "E10+", "T", "M"))

#levels(nintendo_esrb$Rating)

nintendoconsoles <- nintendoconsoles[!is.na(nintendoconsoles$Rating), ]

p4 <- ggplot(data = nintendoconsoles, aes(x = Genre)) +
    geom_bar(aes(fill = Rating), position = "dodge")+
  labs(title="Nintendo ESRB Ratings by Genre",
         x="Genre",
         y="Count")+
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

p4
```


All ESRB ratings by genre
```{r}
videogamesales$Rating <- factor(videogamesales$Rating, levels=c(levels="E", "E10+", "T", "M"))

#newdat <- dat[!is.na(dat$Factor), ]

# remove NA factors
videogamesales <- videogamesales[!is.na(videogamesales$Rating), ]

levels(videogamesales$Rating)

p3 <- ggplot(data = videogamesales, aes(x = Genre)) +
    geom_bar(aes(fill = Rating), position = "dodge")+
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
  labs(title="All ESRB Ratings by Genre",
         x="Genre",
         y="Count")

p5 <- ggplot(data = videogamesales, aes(x = Genre)) +
    geom_bar(aes(fill = Rating), position = "dodge")+
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
  labs(title="All ESRB Ratings by Genre",
         x="Genre",
         y="Count")

p3
```

esrb stats
```{r}
head(subset(mtcars, select = 'gear'))

# industry esrb
count(videogamesales, 'Rating')
3991+1420+2961+1563 #9935
3991/9935 #40.17%

# nintendo esrb
count(nintendoconsoles, 'Rating')
208/309 #67.31% of Nintendo games have E rating


2163+675+642+115 #3595
2163/3595 #60.17 %
```

clean esrb
```{r}
#tedtalks$TransHasMusic <- factor(tedtalks$TransHasMusic, levels=c(levels(tedtalks$TransHasMusic), "1"))

nintendo_esrb$Rating <- factor(nintendo_esrb$Rating, levels=c(levels="E", "E10+", "T", "M"))

levels(nintendo_esrb$Rating)
```

common plot for ESRB
```{r}
library(ggpubr)

#ncol=2

ggarrange(p3, p4, ncol=2, nrow=2, common.legend = TRUE, legend="top")

#figure <- ggarrange(p3, p4, common.legend=TRUE,
 #                   labels = c("A", "B",
 #                   ncol = 2, nrow = 2))
#figure
```

ESRB E Rating 
```{r}

```

```{r}
ggplot(data = nintendo_esrb, aes(x = Genre)) +
    geom_bar(aes(fill = Rating), position = "dodge")+
  labs(title="Nintendo ESRB Ratings by Genre",
         x="Genre",
         y="Count")
```


nintendo publishers
```{r}
nintendoconsole <- 
table(nintendo$Publisher)



unique(videogamesales$Platform)


nintendoconsoles <- videogamesales %>% filter(Platform == "GB" | Platform == "DS" | Platform == "GBA" | Platform == "3DS" | Platform == "Wii" | Platform == "NES" | Platform == "SNES" | Platform == "N64" | Platform == "WiiU" | Platform == "GC")

nintendo_console_publishers <- as.data.frame(table(nintendoconsoles$Publisher))

sum(nintendo_console_publishers$Freq) #6271 total nintendo games across all consoles 
unique(nintendo_console_publishers$Var1) # 582 unique nintendo console publishers

# nintendo is a  publisher in 706 of the 6271 total nintendo games across nintendo consoles games. 11.26% of all nintendo games are published by nintendo


BCI_percent <- BCI / rowSums(BCI) * 100

nintendo_percent <- nintendoconsoles/rowSums(nintendoconsoles) *100


```


