---
title: "IST687 Project"
author: 
- "Jon Kaplan" 
- "Jeffrey Bertucci"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: word_document
---


```{r, echo=TRUE, message=FALSE}

library(tidyverse)
library(lubridate)
library(plotly)
library(kernlab)
library(randomForest)



```


Importing the Data:
```{r}

#LOADING IN THE DATA:

#1) all the GAME data
OutdoorStadium <- c("Open", "Outdoor", "Outdoors", "Outside", "Retr. Roof - Open", "outdoor", "Oudoor","Ourdoor", "Outddors", "Outdor", "outdoor", "Outdor")

IndoorStadium <- c("Dome", "Indoors", "Retr. Roof - Closed", "Indoor", "Closed Dome", "Dome, closed", "Domed, closed", "Indoor, non-retractable roof", "Indoors Domed")


gamedata <- read_csv("IST687 Final Project/game_data.csv") 
gamedata <- gamedata %>% 
   mutate(StadiumType2=case_when(StadiumType %in% OutdoorStadium~"Outdoor",
                                StadiumType %in% IndoorStadium~"Indoor",
                                TRUE~"Unknown")) 



#2) CONCUSSION data
videoreview <- read_csv("IST687 Final Project/video_review.csv")
videoreview <- videoreview %>% 
  mutate(Concussion= 1) #add concussion field with 1 value



#videoreview$Concussion <- as.numeric(videoreview$Concussion)

#3) PLAY level data (score and play description), converted game clock to minutes and seconds since was hms format before
playinformation <- read_csv("IST687 Final Project/play_information.csv", col_types=cols(Game_Date=col_skip(), Game_Clock=col_time(format = "%M:%S")))

#4) read in all player roles in punt plays
playplayerrole <- read_csv("IST687 Final Project/play_player_role_data.csv") 

#read in just punters and punt returners
playplayerrolepunts <- read_csv("IST687 Final Project/play_player_role_data.csv")   %>% 
  dplyr::filter(Role=="P" | Role=="PR")




#JOINING the data into one master file
puntmaster <- gamedata %>% inner_join(playinformation, by=c("GameKey", "Season_Year", "Season_Type", "Week")) %>%
  inner_join(playplayerrole, by=c("GameKey", "Season_Year", "PlayID")) %>% 
  left_join(videoreview) %>% 
  mutate(Quarter=as.factor(Quarter)) %>% 
  mutate(Concussion=if_else(is.na(Concussion), 0, 1))


#combining gamedata and videoreview for more game day information about concussion games


gamevideo <- inner_join(gamedata, videoreview) %>% 
  select(-Game_Date) 



```

```{r}

#OPTIONAL STUFF/notes from importing

#%>% 
  #mutate(FullGameClock=((Quarter-1)*15+Game_Clock))

#sums the total concussions in concussions column of puntmaster
#sum(puntmaster$Concussion, na.rm = TRUE)


#taking NA in concussions field and replacing with 0

#puntmaster[is.na(puntmaster$Concussion),] <- 0
#puntmaster %>% filter(is.na(Concussion))


#OPTIONAL STUFF:


#trying to figure out how to make gameclock for full 60 minutes intead of just quarters
#playgamevideo <- left_join(playinformation, gamevideo) %>% 
  #mutate(FullGameClock=hms((Quarter-1)*15+Game_Clock))




```

Importing the NGS Data:

#importing data

#since NGS data is so massive, tried to create a way to import and also remove previous dataset that is imported

#2016 import
NGS2016Post <- read_csv("NGS-2016-post.csv", col_types = cols(Event=col_character())) 

  
NGS2016Pre <- read_csv("NGS-2016-pre.csv", col_types = cols(Event=col_character()))

NGSData <- dplyr::union(NGS2016Post, NGS2016Pre)
rm(NGS2016Post, NGS2016Pre)
  
NGS2016RegPart1 <- read_csv("NGS-2016-reg-wk1-6.csv", col_types = cols(Event=col_character()))

NGSData <- dplyr::union(NGSData, NGS2016RegPart1)
rm(NGS2016RegPart1)

NGS2016RegPart2 <- read_csv("NGS-2016-reg-wk7-12.csv", col_types = cols(Event=col_character()))

NGSData <- dplyr::union(NGSData, NGS2016RegPart2)
rm(NGS2016RegPart2)

NGS2016RegPart3 <- read_csv("NGS-2016-reg-wk13-17.csv", col_types = cols(Event=col_character()))

NGSData <- dplyr::union(NGSData, NGS2016RegPart3)
rm(NGS2016RegPart3)

#2017 import
NGS2017Post <- read_csv("NGS-2017-post.csv", col_types = cols(Event=col_character()))

NGSData <- dplyr::union(NGSData, NGS2017Post)
rm(NGS2017Post)

NGS2017Pre <- read_csv("NGS-2017-pre.csv", col_types = cols(Event=col_character()))

NGSData <- dplyr::union(NGSData, NGS2017Pre)
rm(NGS2017Pre)

NGS2017Part1 <- read_csv("NGS-2017-reg-wk1-6.csv", col_types = cols(Event=col_character()))

NGSData <- dplyr::union(NGSData, NGS2017Part1)
rm(NGS2017Part1)

NGS2017Part2 <- read_csv("NGS-2017-reg-wk7-12.csv", col_types = cols(Event=col_character()))

NGSData <- dplyr::union(NGSData, NGS2017Part2)
rm(NGS2017Part2)

NGS2017Part3 <- read_csv("NGS-2017-reg-wk13-17.csv", col_types = cols(Event=col_character()))

NGSData <- dplyr::union(NGSData, NGS2017Part3)
rm(NGS2017Part3)



#join player roles with NGS data
NGSPlayerRole <- inner_join(NGS2016Post, playplayerrole) 

#join player roles with NGS data, only Punt and Punt Returner roles
NGSPlayerRolePRP <- inner_join(NGSData, playplayerrolepunts) 



#used union function 
#NGSPlayerRole <- inner_join(playplayerrole, NGS2016Post) %>% 
 # union(inner_join(playplayerrole, NGS2016Pre))

#NGSPlayerRole <- inner_join(playplayerrole, NGS2016Post) %>% 
 # dplyr::union(inner_join(playplayerrole, NGS2016Pre))%>% 
  #dplyr::union(inner_join(playplayerrole, NGS2016RegPart1))%>% 
  #dplyr::union(inner_join(playplayerrole, NGS2016RegPart2))%>% 
  #dplyr::union(inner_join(playplayerrole, NGS2016RegPart3))%>% 
  #dplyr::union(inner_join(playplayerrole, NGS2017Post))%>% 
  #dplyr::union(inner_join(playplayerrole, NGS2017Pre))%>% 
  #dplyr::union(inner_join(playplayerrole, NGS2017Part1))%>% 
  #dplyr::union(inner_join(playplayerrole, NGS2017Part2))%>% 
  #dplyr::union(inner_join(playplayerrole, NGS2017Part3))

#66,492,490 observations in NGS data


#OPTIONAL STUFF:

#remove all unnecessary data after joined
#rm(NGS2016Pre, NGS2016Post, NGS2016RegPart1, NGS2016RegPart2, NGS2016RegPart3, NGS2017Post, NGS2017Pre, NGS2017Part1, NGS2017Part2, NGS2017Part3)
   

#joining concussion occurences from gamevideo and adding velocities and speed data from NGSPlayerRole
#ConcussionNGS <- inner_join(gamevideo, NGSPlayerRolePRP)

            

#events
#ConcussionNGS[!is.na(ConcussionNGS$Event),]
  
 






Average Temperature for Concussions
```{r}
averagetempconcussions <- mean(gamevideo$Temperature)
averagetempconcussions

#60.73 degrees

```

Season Type Count
```{r}
#analysis of where concussions occurred during season
seasontype <- gamevideo$SeasonType
gamevideo %>% group_by(Season_Type) %>% count()




```

Stadium type count
```{r}
#analysis of outdoor vs indoor stadiums


  
stadiumtypecounts <- gamedata %>% group_by(StadiumType) %>% count() %>% arrange(desc(n))
view(stadiumtypecounts)

stadiumcount <- gamedata %>% group_by(StadiumType2) %>% count()

```

Turf count
```{r}

#figuring out the different turfs of fields

turfcount <- gamevideo %>% group_by(Turf) %>% count()
turfcount

turfcount2 <- gamedata %>% group_by(Turf) %>% count()
turfcount2




```

Types of Impacts for Concussions:
```{r}

# histogram of types of concussion impacts
ggplot(videoreview, aes(x=Player_Activity_Derived, fill = Primary_Impact_Type))+
  geom_bar(stat = 'Count')+
  ggtitle("Contact Types Resulting in Concussion")+
  xlab(NULL)

videoreview %>% group_by(Primary_Impact_Type) %>% count()
       
```

Punts per Team
```{r}

#looking at amount of punts by team to get general overview

# punts per team, orientation changed

playinformationsummary <- playinformation %>% 
  group_by(Poss_Team) %>% 
  summarize(NumPunts=n())

#can change color to fill if want different color
ggplot(playinformationsummary, aes(x=reorder(Poss_Team, NumPunts), y=NumPunts, color=Poss_Team))+
  geom_col(width=.7)+coord_flip()+
  ggtitle("Number of Punts per Team")+
  xlab("Teams")+
  ylab("Count")+
  theme(legend.position="none")

#37/6681
#0.55% chance of a concussion on each punt 
```




Player Roles and Concussion
```{r}

#finding out what player role types most affected by punt concussions

concussedroles <- puntmaster %>% 
  filter(Concussion == 1) %>% 
  group_by(Role) %>% 
  summarize(NumConcussions=n())


ggplot(concussedroles, aes(x=reorder(Role, -NumConcussions), y=NumConcussions, color=Role))+
  geom_col(width=.7)+
  ggtitle("Number of Concussions by Player Role")+
  xlab("Role")+
  ylab("Count")+
  theme(legend.position="none")


```

Distance between Punt and Punt Returner


#using the NGS data to find out what distance is between Punt and punt returner on punt plays, seeing if distance is a factor in punt concussions

#use NGSData with filter for only P and PR roles

#find way to figure out which field to filter by, decide on "punt"
unique(NGSPlayerRolePRP$Event)

#rename x and y for P and PR specific
ngspunt <- NGSPlayerRolePRP %>% filter(Event=="punt", Role=="P") %>% 
  rename(XP=x, YP=y)

ngspr <- NGSPlayerRolePRP %>% filter(Event=="punt", Role=="PR") %>% 
  rename(XPR=x, YPR=y)

#use distance formula to calculate using X and Y
prpdist <- inner_join(ngspunt, ngspr, by=c("GameKey", "Season_Year", "Time", "PlayID")) %>% 
  mutate(Distance=sqrt((XP-XPR)^2+(YP-YPR)^2))

#new data with concussions joined
prpdistconc <- inner_join(prpdist, videoreview, by=c("GameKey", "PlayID", "Season_Year"))

#linear regression
#glm()

#distmodel <- glm(Concussion~Distance, data=prpdistconc, family=binomial())
#summary(distmodel)

range(prpdist$Distance)
#24.15795 - 74.91791

range(prpdistconc$Distance)
#41.44668 - 69.59000

mean(prpdistconc$Distance)
#57.50733

mean(prpdist$Distance)
#56.62935

mean(gamedata$Temperature)


#boxplot
ggplot(prpdistconc, aes(x=Concussion, y=Distance)) + geom_boxplot()


puntmasterdistance <- inner_join(puntmaster, prpdist)

#boxplot
ggplot(puntmasterdistance, aes(x=Concussion==1, y=Distance)) + geom_boxplot()




Regression Comparing Game_Day, Temperature, Turf, and Quarter
```{r}
#glm()
#?glm()

model1 <- glm(Concussion~Temperature+Game_Day+Turf, data=puntmaster, family=binomial())
summary(model1)

model2 <- glm(Concussion~Temperature, data=puntmaster, family=binomial())
summary(model2)

model3 <- glm(Concussion~Game_Day, data=puntmaster, family=binomial())
summary(model3)

model4 <- glm(Concussion~Turf, data=puntmaster, family=binomial())
summary(model4)

#(intercept) is quarter 1 in summary because converted to factors
model5 <- glm(Concussion~Quarter, data=puntmaster, family=binomial())
summary(model5)
#Quarter 3 is significant, 0.0428



```

Animated plot


#decided to create an animated plot for player positions during concussion plays

#used tidyverse, plotly, lubridate packages

#create vectors for receiving and punting coverage, 4 variables for plot
rec <- c("PDR1", "PDR2", "PDR3", "PDL3", "PDL2", "PDL1", "PLR", "PLM", "PLL", "VL", "VRi", "VRo", "PFB")

punt <- c("GL", "PLW", "PLT", "PLG", "PLS", "PRG", "PRT", "PRW", "GR", "PC", "PPR", "PPL")

p <- c("P")

pr <- c("PR")


#EXAMPLE 1
#going to animate an instance of PR being concussed, helmet to helmet impact


playplayerrolepunter <- read_csv("IST687 Final Project/play_player_role_data.csv")   %>% 
  dplyr::filter(Role=="PR") #filter just PR

justpunter <- inner_join(gamevideo, playplayerrolepunter) #join concussion data with just PR

gamevideoroles <- inner_join(gamevideo, playplayerrole) #get all roles

#load data
NGS2016RegPart2 <- read_csv("NGS-2016-reg-wk7-12.csv", col_types = cols(Event=col_character()))

input <- readr::read_csv("NGS-2016-reg-wk7-12.csv", col_types = cols(Event=col_character())) %>% 
  dplyr::filter(PlayID==3509) 

input2 <- inner_join(input, playplayerrole) %>% 
  mutate(Side=case_when(Role %in% rec~"Punt Return",
                                           Role %in% punt~"Punt Coverage",
                                           Role == p~"Punter",
                                           Role == pr~"Punt Returner")) %>% 
  mutate(display_time=as.numeric(Time-min(Time)))

# build the plot
p <- ggplot2::ggplot(input2, ggplot2::aes(x = x, 
                                         y = y, 
                                         color = Side,
                                         ids = GSISID,
                                         frame = display_time)) +
  ggplot2::geom_point(size = 3, alpha = .6) +
  ggplot2::geom_text(ggplot2::aes(label = Role), size = 1.5, color = 'black') +
  ggplot2::theme_minimal() +
  ggplot2::theme(legend.position = "none")

# display the plot
p

# convert the ggplot into a plotly
animated_p <- plotly::ggplotly(p) %>%
  plotly::animation_opts(frame = 100)

# execute
animated_p


#EXAMPLE2

#helmet to body impact concussion on position PLW

input3 <- readr::read_csv("NGS-2016-pre.csv", col_types = cols(Event=col_character())) %>% 
  dplyr::filter(PlayID==3129) 

input4 <- inner_join(input, playplayerrole) %>% 
  mutate(Side=case_when(Role %in% rec~"Punt Return",
                                           Role %in% punt~"Punt Coverage",
                                           Role == p~"Punter",
                                           Role == pr~"Punt Returner")) %>% 
  mutate(display_time=as.numeric(Time-min(Time)))



#finds all unique values for punt return and punt coverage
#unique(input2[input2$Side=="Punt Return",]$Role)
#unique(input2[input2$Side=="Punt Coverage",]$Role)



  
# build the plot
p2 <- ggplot2::ggplot(input4, ggplot2::aes(x = x, 
                                         y = y, 
                                         color = Side,
                                         ids = GSISID,
                                         frame = display_time)) +
  ggplot2::geom_point(size = 3, alpha = .6) +
  ggplot2::geom_text(ggplot2::aes(label = Role), size = 1.5, color = 'black') +
  ggplot2::theme_minimal() +
  ggplot2::theme(legend.position = "none")

# display the plot
p2

# convert the ggplot into a plotly
animated_p2 <- plotly::ggplotly(p) %>%
  plotly::animation_opts(frame = 100)

# execute
animated_p2

#found this idea from here:
#http://jimkloet.com/animated_nfl_play.html






Machine learning


#used kernlab and randomForest


puntmaster <- gamedata %>% inner_join(playinformation, by=c("GameKey", "Season_Year", "Season_Type", "Week")) %>%
  inner_join(playplayerrole, by=c("GameKey", "Season_Year", "PlayID")) %>% 
  left_join(videoreview) %>% 
  mutate(Quarter=as.factor(Quarter)) %>% 
  mutate(Concussion=if_else(is.na(Concussion), 0, 1))

puntmaster2<-puntmaster

rem<-c(1,2, 5, 7, 9:14, 18, 20, 21, 23, 25:27, 29, 30, 32:37)

right = function (string, char){
  substr(string,nchar(string)-(char-1),nchar(string))
}

left = function (string,char){
  substr(string,1,char)
}
puntmaster2$Score_Home_Visiting<-as.character(puntmaster2$Score_Home_Visiting)
#puntmaster2<-puntmaster2[, -rem]

puntmaster2$Score_visiting<-as.numeric(right(puntmaster2$Score_Home_Visiting, 2))
puntmaster2$Score_Home<-as.numeric(left(puntmaster2$Score_Home_Visiting, 2))

puntmaster2$Score_difference<-puntmaster2$Score_Home-puntmaster2$Score_visiting

rem2<-c(11,14,15)

puntmaster2<-puntmaster2[, -rem2]

puntmaster3<-puntmaster2

blanks<-which(puntmaster3$GameWeather=="")
puntmaster3$GameWeather<-as.character(puntmaster3$GameWeather)
puntmaster3$GameWeather[blanks]<-gsub("", "Normal", puntmaster3$GameWeather[blanks])


#Assuming that if no note was made regarding weather, we will describe no note as "normal conditions"
#a different description than "sunny" conditions.

Chance<-c("30% Chance of Rain", "Chance of Showers", 
          "Cloudy with Possible Stray Showers/Thundershowers",
          "Cloudy, chance of rain", "Cloudy, Humid, Chance of Rain", 
          "Partly Cloudy, Chance of Rain 80%", "Rain likely, temps in low 40s.")

puntmaster3$GameWeather<-gsub("30% Chance of Rain", "Chance of Rain", puntmaster3$GameWeather)
puntmaster3$GameWeather<-gsub("Chance of Showers", "Chance of Rain", puntmaster3$GameWeather)
puntmaster3$GameWeather<-gsub("Cloudy with Possible Stray Showers/Thundershowers", "Chance of Rain", puntmaster3$GameWeather)
puntmaster3$GameWeather<-gsub("Cloudy, chance of rain", "Chance of Rain", puntmaster3$GameWeather)
puntmaster3$GameWeather<-gsub("Cloudy, Humid, Chance of Rain", "Chance of Rain", puntmaster3$GameWeather)
puntmaster3$GameWeather<-gsub("Partly Cloudy, Chance of Rain 80%", "Chance of Rain", puntmaster3$GameWeather)
puntmaster3$GameWeather<-gsub("Rain likely, temps in low 40s.", "Chance of Rain", puntmaster3$GameWeather)

Rain<-c("Cloudy with periods of rain, thunder possible. Winds shifting to WNW, 10-20 mph.",
        "Cloudy with rain", "Cloudy, Rain", "Light Rain", "Rain", "Showers")

puntmaster3$GameWeather<-gsub("Cloudy with periods of rain, thunder possible. Winds shifting to WNW, 10-20 mph.", "Rain", puntmaster3$GameWeather)
puntmaster3$GameWeather<-gsub("Cloudy with rain", "Rain", puntmaster3$GameWeather)
puntmaster3$GameWeather<-gsub("Cloudy, Rain", "Rain", puntmaster3$GameWeather)
puntmaster3$GameWeather<-gsub("Light Rain", "Rain", puntmaster3$GameWeather)
puntmaster3$GameWeather<-gsub("Rain", "Rain", puntmaster3$GameWeather)
puntmaster3$GameWeather<-gsub("Showers", "Rain", puntmaster3$GameWeather)

#For cloud coverage, basically if it is the only thing of note.
Cloudy<-c("cloudy", "Cloudy", "Cloudy and cold", "Cloudy and Cold", 
          "Cloudy, steady temps", "Coudy", "Mostly cloudy", "Mostly Cloudy",
          "Mostly CLoudy", "Mostly Coudy")

puntmaster3$GameWeather<-gsub("cloudy", "Cloudy", puntmaster3$GameWeather)
puntmaster3$GameWeather<-gsub("Cloudy", "Cloudy", puntmaster3$GameWeather)
puntmaster3$GameWeather<-gsub("Cloudy and cold", "Cloudy", puntmaster3$GameWeather)
puntmaster3$GameWeather<-gsub("Cloudy and Cold", "Cloudy", puntmaster3$GameWeather)
puntmaster3$GameWeather<-gsub("Cloudy, steady temps", "Cloudy", puntmaster3$GameWeather)
puntmaster3$GameWeather<-gsub("Mostly cloudy", "Cloudy", puntmaster3$GameWeather)
puntmaster3$GameWeather<-gsub("Mostly Cloudy", "Cloudy", puntmaster3$GameWeather)
puntmaster3$GameWeather<-gsub("Mostly CLoudy", "Cloudy", puntmaster3$GameWeather)
puntmaster3$GameWeather<-gsub("Mostly Coudy", "Cloudy", puntmaster3$GameWeather)
puntmaster3$GameWeather<-gsub("Coudy", "Cloudy", puntmaster3$GameWeather)

Thunder<-c("T-Storms", "Scattered thunderstorms")

puntmaster3$GameWeather<-gsub("T-Storms", "Thunder Storms", puntmaster3$GameWeather)
puntmaster3$GameWeather<-gsub("Scattered thunderstorms", "Thunder Storms", puntmaster3$GameWeather)

#distinguishing clear/normal from sunny, mentality->clear means peak football conditions all around
Sunny<-c("Suny", "Sunny, highs to upper 80s", "Sunny Skies", "Sunny Intervals", 
         "Sunny intervals", "Sunny and warm", "Sunny and cool", "Sunny and Clear", 
         "Sunny", "Sun & clouds", "Sunny", "Party Cloudy", "Partly Sunny", "Partly sunny",
         "Partly Cloudy, lows to upper 50s.", "Partly CLoudy", "Partly Cloudy", "Mostly Sunny")

puntmaster3$GameWeather<-gsub("Suny", "Sunny", puntmaster3$GameWeather)
puntmaster3$GameWeather<-gsub("Sunny, highs to upper 80s", "Sunny", puntmaster3$GameWeather)
puntmaster3$GameWeather<-gsub("Sunny Skies", "Sunny", puntmaster3$GameWeather)
puntmaster3$GameWeather<-gsub("Sunny Intervals", "Sunny", puntmaster3$GameWeather)
puntmaster3$GameWeather<-gsub("Sunny intervals", "Sunny", puntmaster3$GameWeather)
puntmaster3$GameWeather<-gsub("Sunny and warm", "Sunny", puntmaster3$GameWeather)
puntmaster3$GameWeather<-gsub("Sunny and cool", "Sunny", puntmaster3$GameWeather)
puntmaster3$GameWeather<-gsub("Sunny and Clear", "Sunny", puntmaster3$GameWeather)
puntmaster3$GameWeather<-gsub("Sun & clouds", "Sunny", puntmaster3$GameWeather)
puntmaster3$GameWeather<-gsub("Sunny", "Sunny", puntmaster3$GameWeather)
puntmaster3$GameWeather<-gsub("Party Cloudy", "Sunny", puntmaster3$GameWeather)
puntmaster3$GameWeather<-gsub("Partly Sunny", "Sunny", puntmaster3$GameWeather)
puntmaster3$GameWeather<-gsub("Partly sunny", "Sunny", puntmaster3$GameWeather)
puntmaster3$GameWeather<-gsub("Partly Cloudy, lows to upper 50s.", "Sunny", puntmaster3$GameWeather)
puntmaster3$GameWeather<-gsub("Partly CLoudy", "Sunny", puntmaster3$GameWeather)
puntmaster3$GameWeather<-gsub("Partly Cloudy", "Sunny", puntmaster3$GameWeather)
puntmaster3$GameWeather<-gsub("Mostly Sunny", "Sunny", puntmaster3$GameWeather)
puntmaster3$GameWeather<-gsub("Sunny", "Sunny", puntmaster3$GameWeather)

Snow<-c("Snow showers", "Snow", "Heavy lake effect snow", "Snow Rain, 3 to 5 inches expected.", 
        "Cloudy, light snow accumulating 1-3", "Snow")

puntmaster3$GameWeather<-gsub("Snow", "Snow", puntmaster3$GameWeather)
puntmaster3$GameWeather<-gsub("Snow showers", "Snow", puntmaster3$GameWeather)
puntmaster3$GameWeather<-gsub("Heavy lake effect snow", "Snow", puntmaster3$GameWeather)
puntmaster3$GameWeather<-gsub("Snow Rain, 3 to 5 inches expected.", "Snow", puntmaster3$GameWeather)
puntmaster3$GameWeather<-gsub('Cloudy, light snow accumulating 1-3"', "Snow", puntmaster3$GameWeather)


fog<-c("Cloudy, fog started developing in 2nd quarter", "Cloudy with patches of fog")

puntmaster3$GameWeather<-gsub("Cloudy, fog started developing in 2nd quarter", "Foggy", puntmaster3$GameWeather)
puntmaster3$GameWeather<-gsub("Cloudy with patches of fog", "Foggy", puntmaster3$GameWeather)

#Clear is a catch-all at the end, essentially meaning "no weather to report". Thats good football.
Clear<-c("Clear", "CLEAR", "Clear and Cold", "Clear and cool", "Clear and warm", 
         "Clear skies", "Clear Skies", "Cold", "Fair", "Mostly Clear. Gusting ot 14.", 
         "Normal")

puntmaster3$GameWeather<-gsub("Clear", "Clear", puntmaster3$GameWeather)
puntmaster3$GameWeather<-gsub("CLEAR", "Clear", puntmaster3$GameWeather)
puntmaster3$GameWeather<-gsub("Clear and Cold", "Clear", puntmaster3$GameWeather)
puntmaster3$GameWeather<-gsub("Clear and cool", "Clear", puntmaster3$GameWeather)
puntmaster3$GameWeather<-gsub("Clear and warm", "Clear", puntmaster3$GameWeather)
puntmaster3$GameWeather<-gsub("Clear skies", "Clear", puntmaster3$GameWeather)
puntmaster3$GameWeather<-gsub("Clear Skies", "Clear", puntmaster3$GameWeather)
puntmaster3$GameWeather<-gsub("Cold", "Clear", puntmaster3$GameWeather)
puntmaster3$GameWeather<-gsub("Fair", "Clear", puntmaster3$GameWeather)
puntmaster3$GameWeather<-gsub("Mostly Clear. Gusting ot 14.", "Clear", puntmaster3$GameWeather)
puntmaster3$GameWeather<-gsub("Normal", "Clear", puntmaster3$GameWeather)

Hazy<-c("Hazy, hot and humid", "Hazy")

puntmaster3$GameWeather<-gsub("Hazy, hot and humid", "Hazy", puntmaster3$GameWeather)
puntmaster3$GameWeather<-gsub("Hazy", "Hazy", puntmaster3$GameWeather)

puntmaster3$GameWeather<-gsub("Indoor", "Indoors", puntmaster3$GameWeather)
puntmaster3$GameWeather<-gsub("Indoorss", "Indoors", puntmaster3$GameWeather)


puntmaster3$GameWeather<-as.factor(puntmaster3$GameWeather)


puntmaster3$Week<-as.factor(puntmaster3$Week)

#Similar to Weather, Turf needs to be normalized

blanks2<-which(puntmaster3$Turf=="")
puntmaster3$Turf<-as.character(puntmaster3$Turf)
puntmaster3$Turf[blanks2]<-gsub("", "Natural Grass", puntmaster3$Turf[blanks2])

Astroturf<-c("A-Turf Titan", "Artifical", "Artificial", "AstroTurf GameDay Grass 3D", 
             "DD GrassMaster", "Synthetic", "UBU Speed Series-S5-M", "UBU Speed Series S5-M", 
             "UBU Sports Speed S5-M", "Field turf", "Field Turf", "FieldTurf", "FieldTurf360",
             "Synthetic 360", "Synthetic360")

puntmaster3$Turf<-gsub("A-Turf Titan", "Synthetic", puntmaster3$Turf)
puntmaster3$Turf<-gsub("Artifical", "Synthetic", puntmaster3$Turf)
puntmaster3$Turf<-gsub("Artificial", "Synthetic", puntmaster3$Turf)
puntmaster3$Turf<-gsub("AstroTurf GameDay Grass 3D", "Synthetic", puntmaster3$Turf)
puntmaster3$Turf<-gsub("DD GrassMaster", "Synthetic", puntmaster3$Turf)
puntmaster3$Turf<-gsub("Synthetic", "Synthetic", puntmaster3$Turf)
puntmaster3$Turf<-gsub("UBU Speed Series-S5-M", "Synthetic", puntmaster3$Turf)
puntmaster3$Turf<-gsub("UBU Speed Series S5-M", "Synthetic", puntmaster3$Turf)
puntmaster3$Turf<-gsub("UBU Sports Speed S5-M", "Synthetic", puntmaster3$Turf)
puntmaster3$Turf<-gsub("Field turf", "Synthetic", puntmaster3$Turf)
puntmaster3$Turf<-gsub("Field Turf", "Synthetic", puntmaster3$Turf)
puntmaster3$Turf<-gsub("FieldTurf", "Synthetic", puntmaster3$Turf)
puntmaster3$Turf<-gsub("FieldTurf360", "Synthetic", puntmaster3$Turf)
puntmaster3$Turf<-gsub("Synthetic 360", "Synthetic", puntmaster3$Turf)
puntmaster3$Turf<-gsub("Synthetic360", "Synthetic", puntmaster3$Turf)

Natural<-c("grass", "Grass", "Natrual Grass", "Natural", "Natural grass", "Natural Grass",
           "Natural Grass ", "Naturall Grass", "Natrual Natural", "Natural Natural", 
           "Natural Natural", "Naturall Natural", "Natural ")

puntmaster3$Turf<-gsub("grass", "Natural", puntmaster3$Turf)
puntmaster3$Turf<-gsub("Grass", "Natural", puntmaster3$Turf)
puntmaster3$Turf<-gsub("Natrual Grass", "Natural", puntmaster3$Turf)
puntmaster3$Turf<-gsub("Natural", "Natural", puntmaster3$Turf)
puntmaster3$Turf<-gsub("Natural grass", "Natural", puntmaster3$Turf)
puntmaster3$Turf<-gsub("Natural Grass", "Natural", puntmaster3$Turf)
puntmaster3$Turf<-gsub("Natural Grass ", "Natural", puntmaster3$Turf)
puntmaster3$Turf<-gsub("Naturall Grass", "Natural", puntmaster3$Turf)

puntmaster3$Turf<-gsub("Natrual Natural", "Natural", puntmaster3$Turf)
puntmaster3$Turf<-gsub("Natural Natural", "Natural", puntmaster3$Turf)
puntmaster3$Turf<-gsub("Natural Natural", "Natural", puntmaster3$Turf)
puntmaster3$Turf<-gsub("Naturall Natural", "Natural", puntmaster3$Turf)
puntmaster3$Turf<-gsub("Natural ", "Natural", puntmaster3$Turf)


puntmaster3$Turf<-as.factor(puntmaster3$Turf)
summary(puntmaster3$Turf)

puntmaster3$Temperature<-as.numeric(puntmaster3$Temperature)

puntmaster3$StadiumType2<-as.factor(puntmaster3$StadiumType2)

puntmaster3$Score_difference<-as.factor(puntmaster3$Score_difference)

puntmaster3$Concussion<-as.factor(puntmaster3$Concussion)

puntmaster3$Start_Time<-as.numeric(puntmaster3$Start_Time)

#regulating all indoor weather and temperature to account for weird readings, averaging at 70 degrees
puntmaster3$GameWeather[which(puntmaster3$StadiumType2=="Indoor")] <-"Indoor"
puntmaster3$Temperature[which(puntmaster3$StadiumType2=="Indoor")] <-"70"

puntmaster4<-puntmaster3

#removing NAs, these are mostly temperature, none of the NAs had concussions

puntmasterna<-complete.cases(puntmaster4)

puntmaster4<-puntmaster4[puntmasterna,]

puntmaster4$Score_difference<-as.numeric(puntmaster4$Score_difference)

puntmaster4$Week<-as.numeric(puntmaster4$Week)

puntmaster4$Quarter<-as.numeric(puntmaster4$Quarter)

puntmaster4$Role<-as.character(puntmaster4$Role)

puntmaster4$Role<-as.factor(puntmaster4$Role)

puntmaster4$Turf<-gsub("Natural", 1, puntmaster4$Turf)
puntmaster4$Turf<-gsub("Synthetic", 0, puntmaster4$Turf)

puntmaster4$NaturalTurf<-puntmaster4$Turf

puntmaster4<-puntmaster4[,-4]

puntmaster4$NaturalTurf<-as.numeric(puntmaster4$NaturalTurf)

#times are very difficult to parse, removing them
puntmaster4<-puntmaster4[,-c(4, 9)]

#categorizing weather conditions into 3 groups 1, 2, 3: Optimal, Suboptimal, Bad
summary(puntmaster4$GameWeather)

Optimal<-c("Clear", "Cloudy", "Indoors", "Sunny")

puntmaster4$GameWeather<-gsub("Clear", 1, puntmaster4$GameWeather)
puntmaster4$GameWeather<-gsub("Cloudy", 1, puntmaster4$GameWeather)
puntmaster4$GameWeather<-gsub("Indoors", 1, puntmaster4$GameWeather)
puntmaster4$GameWeather<-gsub("Sunny", 1, puntmaster4$GameWeather)

SubOptimal<-c("Chance of Rain", "Hazy", "Foggy")

puntmaster4$GameWeather<-gsub("Chance of Rain", 2, puntmaster4$GameWeather)
puntmaster4$GameWeather<-gsub("Hazy", 2, puntmaster4$GameWeather)
puntmaster4$GameWeather<-gsub("Foggy", 2, puntmaster4$GameWeather)

Bad<-c("Rain", "Snow", "Thunder Storms")

puntmaster4$GameWeather<-gsub("Rain", 3, puntmaster4$GameWeather)
puntmaster4$GameWeather<-gsub("Snow", 3, puntmaster4$GameWeather)
puntmaster4$GameWeather<-gsub("Thunder Storms", 3, puntmaster4$GameWeather)

puntmaster4$GameWeather<-as.factor(puntmaster4$GameWeather)
puntmaster4$NaturalTurf<-as.factor(puntmaster4$NaturalTurf)

summary(puntmaster4$NaturalTurf)

puntmasterna<-complete.cases(puntmaster4)

puntmaster4<-puntmaster4[puntmasterna,]

which(puntmasterna==FALSE)

randindex<-sample(1:dim(puntmaster4)[1])
traindata<-puntmaster4[randindex[1:8856],]
testdata<-puntmaster4[randindex[8857:13284],]

rm(gamedata, playinformation, playplayerrole)

#Running a random forest based on our most recent data frame. He's not good, but he is trying.
#The problem is trying to predict a small handful of ones in an ocean of zeros 
#is incredibly difficult. We are surprised it even made an 
#attempt to guess at a couple concussion plays

rf<-randomForest(Concussion ~., data=puntmaster4)

sum(rf$err.rate[,2])/length(rf$err.rate)

sum(rf$err.rate[,3])/length(rf$err.rate)

#no benefits from more trees
rf2<-randomForest(Concussion ~., data=puntmaster4, ntree=1000)

#KSVM actually predicts 2 concussion correctly, but gets the rest of the data wrong.
#It guessed concussion on everything, which means there is most likely more, and better factors
#that can predict these concussions, but they may not be in this dataset.
ML2<-ksvm(Concussion~NaturalTurf+Score_difference+Quarter+GameWeather, data=traindata, kernel="polydot", kpar="automatic", C=5, cross=3, prob.model=TRUE)

prediction<-predict(ML2, testdata)

comptable<-data.frame(testdata$Concussion, prediction)

comptable$prediction<-as.numeric(comptable$prediction)

length(which(comptable$prediction==1&comptable$prediction==comptable$testdata.Concussion))
comptable

#Once again, 
#what we are testing for is so small in comparison to our data, it is going to be extremely hard
#to teach a machine to rout out the main causes of these events. But, it may be possible
#with more data.

length(which(puntmaster$Concussion==1))



